---
title: "Data Analysis & Plotting for Thesis"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###### Set working directory 
```{r}
setwd('C:/Users/kilda/OneDrive/THESIS/Scripts')
```

###### Import packages
```{r}
library(dplyr)
library(devtools)
library(tidyverse)
library(stringr)
library(data.table)
library(ggplot2)
library(RColorBrewer)
library(readr)
library(ggthemr)
library(ggthemes)
```

###### Load data 
* please note: not all data wrangling included in script 
```{r}
data_bias <- read_csv("dataset_final_google.csv")
data_gd_google <- read_csv("gender_bias_dict_google.csv") 
```

## Descriptive Analysis 

###### Length of unique words with assigned gender score 
```{r}
newdata <- data_gd_google[ which(data_gd_google$Bias > '-1000'), ]
length(newdata$Bias)
```
###### Density plot 
```{r}
ggplot(data=data_bias, aes(data_bias$man_woman)) + 
  geom_histogram(aes(y =..density..),col="red", fill="green", alpha=.2) + 
  geom_density(col=2) + 
   labs(title="Density Plot of Gender Bias", y = "Density", x = "Gender Bias")
```
###### Find mean bias of data 
```{r}
summary(data_bias$man_woman)
```

###### Find standard deviation 
```{r}
sd(data_bias$man_woman)
```

##### Linear regression models 
```{r}
lm_occu <- lm(man_woman ~ Occupation, data_bias)
summary(lm_occu)
```

```{r}
lm_ind <- lm(man_woman ~ Industry, data_bias)
summary(lm_ind)
```

##### Comparing absolute means of female and male bias 
```{r}
data_bias$mf[data_bias$man_woman <= 0] <- "female"
data_bias$mf[data_bias$man_woman >= 0] <- "male"
data_bias$biases <- "male"
data_bias$biases[data_bias$Industry == "Healthcare & Social Assistance" | data_bias$Industry == "Education & Training"] <- "female"
data_bias$absolute <- abs(data_bias$man_woman)
mean(data_bias$absolute[data_bias$mf == "female"])
mean(data_bias$absolute[data_bias$mf == "male"])
sd(data_bias$absolute[data_bias$mf == "female"])
sd(data_bias$absolute[data_bias$mf == "male"])
data.summary <- data_bias %>%
  group_by(mf) %>%
  summarise(
    sd = sd(absolute, na.rm = TRUE),
    len = mean(absolute)
  )
data.summary

ggplot(data.summary, aes(x = mf, y = len, ymin = len-sd, ymax = len+sd))+
  geom_errorbar(width = 0.2)
```

##### T-Test
```{r}
t.test(data_bias$absolute[data_bias$mf == "male"], data_bias$absolute[data_bias$mf == "female"])
```













## Plotting & Explorative Analysis 
###### Defining colours for industries in plots 
```{r}
cols_ratio <- c("Construction" = "#020873", "Mining" = "#180b77", "Transport Postal and Warehousing" = "#260e7c", "Electricity Gas Water and Waste Services" = "#311180", "Manufacturing" = "#3c1485", "Wholesale Trade" = "#451789", "Agriculture Forestry and Fishing" = "#4e1b8d",  "Information Media and Telecommunications" = "#571f92", "Professional Scientific and Technical Services" = "#602296", "Rental Hiring and Real Estate Services" = "#68269a", "Public Administration and Safety" = "#712a9f", "Financial and Insurance Services" = "#792ea3", "Arts and Recreation Services" = "#8232a7",  "Administrative and Support Services" = "#8a36ab", "Accommodation and Food Services" = "#923aaf", "Retail Trade" = "#9a3eb4", "Education and Training" = "#a343b8", "Healthcare and Social Assistance" = "#ab47bc")
```

#### Industry level plots 
###### Plot - Mean gender bias per industry 
```{r}
ggplot(data_bias, aes(x= reorder(Industry, -man_woman), y=man_woman, label=man_woman, fill = Industry)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Mean Gender Bias per Industry", y = "Gender Bias", x = "Industry") +
  scale_fill_manual(values = cols_ratio)
```
###### Plot - Ratio vs. mean bias 
```{r}
data_bias %>% group_by(Industry) %>% 
  ggplot(aes(mean_bias,Ratio, color=Industry)) + 
  geom_point()+
  geom_smooth(method = "lm")+
  geom_text(aes(label=Industry),hjust=0, vjust=0)+ 
  labs(title="Mean Gender Bias vs. Gender Ratio per Industry", y = "Gender Ratio", x = "Gender Bias") +
  scale_colour_manual(values = cols_ratio)
```

###### Pearson's correlation ratio vs. bias 
```{r}
cor.test(data_bias$Ratio, data_bias$mean_bias, method=c("pearson"))
```
###### Plot - Average salary 2020 vs. gender bias 
```{r}
data_bias %>% group_by(Industry) %>% 
  ggplot(aes(mean_bias,salary_mean2020, color=Industry)) + 
  geom_point()+
  geom_smooth(method = "lm")+
  geom_text(aes(label=Industry),hjust=0, vjust=0)+ 
  labs(title="Mean Gender Bias vs. Mean Salary per Industry", y = "Mean Salary", x = "Gender Bias") +
  scale_colour_manual(values = cols_ratio)
```

###### Pearson's correlation - salary vs. mean bias 
```{r}
cor.test(data_bias$salary_mean2020, data_bias$mean_bias, method=c("pearson"))
```

###### Plot - salary vs. ratio 
```{r}
data_bias %>% group_by(Industry) %>% 
  ggplot(aes(Ratio,salary_mean2020, color=Industry)) + 
  geom_point()+
  geom_smooth(method = "lm")+
  geom_text(aes(label=Industry),hjust=0, vjust=0)+ 
  labs(title="Gender Ratio vs. Mean Salary per Industry", y = "Mean Salary", x = "Gender Ratio") +
  scale_colour_manual(values = cols_ratio)
```
###### Pearson's correlation - salary vs. bias 
```{r}
cor.test(data_bias$salary_mean2020, data_bias$Ratio, method=c("pearson"))
```
###### Plot - GPG vs. mean bias 
```{r}
data_bias %>% group_by(Industry) %>% 
  ggplot(aes(mean_bias,gpg, color=Industry)) + 
  geom_point()+
  geom_smooth(method = "lm")+
  geom_text(aes(label=Industry),hjust=0, vjust=0)+ 
  labs(title="Average Gender Bias vs. GPG per Industry", y = "GPG", x = "Average Gender Bias")+
  scale_colour_manual(values = cols_ratio)
```
###### Pearson's correlation - GPG vs. bias
```{r}
cor.test(data_bias$gpg, data_bias$mean_bias, method=c("pearson"))
```
###### Plot - GPG vs. Ratio 
```{r}

data_bias %>% group_by(Industry) %>% 
  ggplot(aes(Ratio,gpg, color=Industry)) + 
  geom_point()+
  geom_smooth(method = "lm")+
  geom_text(aes(label=Industry),hjust=0, vjust=0)+ 
  labs(title="Gender Ratio vs. GPG per Industry", y = "GPG", x = "Ratio")+
  scale_colour_manual(values = cols_ratio)

```
###### Pearson's correlation - GPG vs. ratio 
```{r}
cor.test(data_bias$gpg, data_bias$Ratio, method=c("pearson"))
```


## Occupation oriented analysis 

###### Plot - gender bias of occupations 
```{r}
# call in dataset where occupations are not duplicated 
data_occ <- read.csv("dataset_final_google_occupations.csv")

#plot 
gg_occ <- ggplot(data_occ, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill=Industry)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
scale_fill_manual(values = cols_ratio) + 
  labs(title="Gender Bias per Occupation", y = "Gender Bias", x = "Occupation")


gg_occ + theme(axis.text = element_text(size = 4))     
```

###### Find orderof occupations by bias 
```{r}
occ_order <- data_bias %>% 
  group_by(Occupation) %>% 
  summarise(mean(man_woman))

#save as csv if you want 
write.csv(occ_order,"occ_order.csv") 
```


###### plotting top 10 occupations 
```{r}
#import subset pf data for top 10 occupations 
data_top10 <- read_csv("dataset_final_google_occupation_top10.csv")

#plot
ggplot(data_top10, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill=Industry)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  scale_fill_manual(values = cols_ratio) + 
  labs(title="Top 10 Male and Female Biased Occupations", y = "Gender Bias", x = "Occupation")
```

###### Industry subsetting 
```{r}
in1 <- subset(data_bias, data_bias$Industry == 'Accommodation and Food Services')
summary(in1$man_woman)

in22 <- subset(data_bias, data_bias$Industry == 'Administrative and Support Services')
summary(in22$man_woman)

in2 <- subset(data_bias, data_bias$Industry == 'Agriculture Forestry and Fishing')
summary(in2$man_woman)

in3 <- subset(data_bias, data_bias$Industry == 'Arts and Recreation Services')
summary(in3$man_woman)

in4 <- subset(data_bias, data_bias$Industry == 'Construction')
summary(in4$man_woman)

in5 <- subset(data_bias, data_bias$Industry == 'Education and Training')
summary(in5$man_woman)

in6 <- subset(data_bias, data_bias$Industry == 'Electricity Gas Water and Waste Services')
summary(in6$man_woman)

in7 <- subset(data_bias, data_bias$Industry == 'Financial and Insurance Services')
summary(in7$man_woman)

in8 <- subset(data_bias, data_bias$Industry == 'Healthcare and Social Assistance')
summary(in8$man_woman)

in9 <- subset(data_bias, data_bias$Industry == 'Information Media and Telecommunications')
summary(in9$man_woman)

in10 <- subset(data_bias, data_bias$Industry == 'Manufacturing')
summary(in10$man_woman)

in11 <- subset(data_bias, data_bias$Industry == 'Mining')
summary(in11$man_woman)

in12 <- subset(data_bias, data_bias$Industry == 'Professional Scientific and Technical Services')
summary(in12$man_woman)

in13 <- subset(data_bias, data_bias$Industry == 'Public Administration and Safety')
summary(in13$man_woman)

in14 <- subset(data_bias, data_bias$Industry == 'Rental Hiring and Real Estate Services')
summary(in14$man_woman)

in15 <- subset(data_bias, data_bias$Industry == 'Retail Trade')
summary(in15$man_woman)

in16 <- subset(data_bias, data_bias$Industry == 'Transport Postal and Warehousing')
summary(in16$man_woman)

in17 <- subset(data_bias, data_bias$Industry == 'Wholesale Trade')
summary(in17$man_woman)

```
###### Plotting occupations by bias in all industries 
```{r}
ggplot(in1, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill = Occupation)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Occupation by Gender Bias - Accommodation and Food Services", y = "Gender Bias", x = "Occupation") + 
  theme_pander() +
  scale_fill_pander()
```
```{r}
ggplot(in22,aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill = Occupation)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Occupation by Gender Bias - Administrative and Support Services", y = "Gender Bias", x = "Occupation") + 
  theme_pander() +
  scale_fill_pander()
```

```{r}
ggplot(in2, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill = Occupation)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Occupation by Gender Bias - Agriculture Forestry and Fishing", y = "Gender Bias", x = "Occupation") + 
  theme_pander() +
  scale_fill_pander()
```
```{r}
ggplot(in3, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill = Occupation)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Occupation by Gender Bias - Arts and Recreation Services", y = "Gender Bias", x = "Occupation") + 
  theme_pander() +
  scale_fill_pander()
```
```{r}
ggplot(in4, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill = Occupation)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Occupation by Gender Bias - Construction", y = "Gender Bias", x = "Occupation")+ 
  theme_pander() +
  scale_fill_pander()
```
```{r}
ggplot(in5, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill = Occupation)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Occupation by Gender Bias - Education and Training", y = "Gender Bias", x = "Occupation") + 
  theme_pander() +
  scale_fill_pander()
```
```{r}
ggplot(in6, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill = Occupation)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Occupation by Gender Bias - Electricity Gas Water and Waste Services", y = "Gender Bias", x = "Occupation")  + 
  theme_pander() +
  scale_fill_pander()
```
```{r}
ggplot(in7, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill = Occupation)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Occupation by Gender Bias - Financial and Insurance Services", y = "Gender Bias", x = "Occupation")  + 
  theme_pander() +
  scale_fill_pander()
```
```{r}
ggplot(in8, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill = Occupation)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Occupation by Gender Bias - Healthcare and Social Assistance", y = "Gender Bias", x = "Occupation") + 
  theme_pander() +
  scale_fill_pander()
```
```{r}
ggplot(in9, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill = Occupation)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Occupation by Gender Bias - Information Media and Telecommunications", y = "Gender Bias", x = "Occupation") + 
  theme_pander() +
  scale_fill_pander()
```
```{r}
ggplot(in10, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill = Occupation)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Occupation by Gender Bias - Manufacturing", y = "Gender Bias", x = "Occupation") + 
  theme_pander() +
  scale_fill_pander()
```
```{r}
ggplot(in11, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill = Occupation)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Occupation by Gender Bias - Mining", y = "Gender Bias", x = "Occupation") + 
  theme_pander() +
  scale_fill_pander()
```
```{r}
ggplot(in12, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill = Occupation)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Occupation by Gender Bias - Professional Scientific and Technical Services", y = "Gender Bias", x = "Occupation") + 
  theme_pander() +
  scale_fill_pander()
```
```{r}
ggplot(in13, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill = Occupation)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Occupation by Gender Bias - Public Administration and Safety", y = "Gender Bias", x = "Occupation") + 
  theme_pander() +
  scale_fill_pander()
```
```{r}
ggplot(in14, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill = Occupation)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Occupation by Gender Bias - Rental Hiring and Real Estate Services", y = "Gender Bias", x = "Occupation") + 
  theme_pander() +
  scale_fill_pander()
```
```{r}
ggplot(in15, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill = Occupation)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Occupation by Gender Bias - Retail Trade", y = "Gender Bias", x = "Occupation") + 
  theme_pander() +
  scale_fill_pander()
```
```{r}
ggplot(in16, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill = Occupation)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Occupation by Gender Bias - Transport Postal and Warehousing", y = "Gender Bias", x = "Occupation") + 
  theme_pander() +
  scale_fill_pander()
```
```{r}
ggplot(in17, aes(x= reorder(Occupation, -man_woman), y=man_woman, label=man_woman, fill = Occupation)) +
  geom_bar(stat='summary', width=.5)  +
  scale_x_discrete(position = "top")+
  coord_flip()+
  labs(title="Occupation by Gender Bias - Wholesale Trade", y = "Gender Bias", x = "Occupation")  + 
  theme_pander() +
  scale_fill_pander()
```












